Medical Concept Extraction

### 2012-12-17 paper/paper.tex
fixed column lines in tables

\begin{figure}[t]
\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|}
	\hline
	\multicolumn{6}{|c|}{\bf crfsuite} \\ \hline
	& & \multicolumn{4}{|c|}{Predicted} \\ \hline
	& & test & problem & none & treatment \\ \hline
	\multirow{4}{*}{\begin{sideways}Actual\end{sideways}}
		& test & 14388 & 1503 & 932 & 414	\\ \hline
		& problem & 288 & 27993 & 1521 & 474	\\ \hline
		& none & 3214 & 18463 & 175032 & 5729	\\ \hline
		& treatment & 304 & 1896 & 1418 & 13680	\\ \hline

@@

\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|}
	\hline
	\multicolumn{6}{|c|}{\bf liblinear} \\ \hline
	& & \multicolumn{4}{|c|}{Predicted} \\ \hline
	& & test & problem & none & treatment \\ \hline
	\multirow{4}{*}{\begin{sideways}Actual\end{sideways}}
		& test & 11819 & 1171 & 3718 & 529	\\ \hline
		& problem & 475 & 22682 & 6383 & 736	\\ \hline
		& none & 1120 & 4408 & 195085 & 1825	\\ \hline
		& treatment & 249 & 1251 & 4099 & 11699	\\ \hline

@@

\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|}
	\hline
	\multicolumn{6}{|c|}{\bf libsvm} \\ \hline
	& & \multicolumn{4}{|c|}{Predicted} \\ \hline
	& & test & problem & none & treatment \\ \hline
	\multirow{4}{*}{\begin{sideways}Actual\end{sideways}}
		& test & 12741 & 1179 & 2935 & 382	\\ \hline
		& problem & 542 & 23288 & 5818 & 628	\\ \hline
		& none & 1284 & 4175 & 195716 & 1263	\\ \hline
		& treatment & 438 & 1989 & 3860 & 11011	\\ \hline

>>>>

\begin{figure}[t]
\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|}
	\hline
	\multicolumn{6}{|c|}{\bf crfsuite} \\ \hline
	& & \multicolumn{4}{|c|}{Predicted} \\ \cline{2-6}
	& & test & problem & none & treatment \\ \cline{2-6}
	\multirow{4}{*}{\begin{sideways}Actual\end{sideways}}
		& test & 14388 & 1503 & 932 & 414	\\ \cline{2-6}
		& problem & 288 & 27993 & 1521 & 474	\\ \cline{2-6}
		& none & 3214 & 18463 & 175032 & 5729	\\ \cline{2-6}
		& treatment & 304 & 1896 & 1418 & 13680	\\ \hline

@@

\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|}
	\hline
	\multicolumn{6}{|c|}{\bf liblinear} \\ \hline
	& & \multicolumn{4}{|c|}{Predicted} \\ \cline{2-6}
	& & test & problem & none & treatment \\ \cline{2-6}
	\multirow{4}{*}{\begin{sideways}Actual\end{sideways}}
		& test & 11819 & 1171 & 3718 & 529	\\ \cline{2-6}
		& problem & 475 & 22682 & 6383 & 736	\\ \cline{2-6}
		& none & 1120 & 4408 & 195085 & 1825	\\ \cline{2-6}
		& treatment & 249 & 1251 & 4099 & 11699	\\ \hline

@@

\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|}
	\hline
	\multicolumn{6}{|c|}{\bf libsvm} \\ \hline
	& & \multicolumn{4}{|c|}{Predicted} \\ \cline{2-6}
	& & test & problem & none & treatment \\ \cline{2-6}
	\multirow{4}{*}{\begin{sideways}Actual\end{sideways}}
		& test & 12741 & 1179 & 2935 & 382	\\ \cline{2-6}
		& problem & 542 & 23288 & 5818 & 628	\\ \cline{2-6}
		& none & 1284 & 4175 & 195716 & 1263	\\ \cline{2-6}
		& treatment & 438 & 1989 & 3860 & 11011	\\ \hline
